Grade Retention and Mixed Race

### 2022-11-17 products/paper/main.qmd
Add concluding paragraph to introduction

The results provide a window into the placement of biracial children within an existing system of racial inequality in our educational systems. <!-- TODO  PITHY SUMMARY -->

>>>>

The results provide a window into the placement of biracial children within an existing system of racial inequality in our educational systems. Given the large sample size I am able to draw, I am able to estimate relatively precise estimates for most biracial groups. In contrast to prevailing hypothesis predicting either a pattern of hypodescent or an in-between position for biracial individuals, I find a consistent pattern in which the risk of grade retention is similar to that of the lower risk constituent monoracial group. This result holds even after adjusting for differences in resources across respondents, despite the fact that most biracial groups are positively selected by parental resources relative to their monoracial group. I discuss the implications for these findings in the conclusions.
